\documentclass[11pt,english,a4paper]{scrartcl}
\input{my_definitions.tex}

\title{Cooperative Manipulators}
\author{Tobias Keute}

\begin{document}
\vfill
\maketitle
\vfill
\pagebreak
\tableofcontents
\pagebreak
\section{Introduction}
	\subsection{What is a Robot? What is a Manipulator?}
	At first sight a \begriff{robot} is very similar to a crane for example. Both are made from several \begriff{links} attached serialy with either revolute or prismatic \begriff{joints}, at both the end effector can be placed in any place in the \begriff{workspace} by defining the \begriff{joint parameters} of each individual joint. The only difference between a robot and a \begriff{manipulator} (the crane) is that the manipulator ist controlled by a human and the robot is guided by an program running on a computer.
%	\include{ArmAlsRoboter.ps}
%
%	
%	
%	\subsection{What is so important about robots being cooperative?}
%\section{Rigid Manipulators}
%\section{Cooperativ Rigid Manipulators}
\section{Flexible Manipulators}
	As the focus of modern manufactoring is more and more on light-weight tecnology, as for example 	
space schiences, the structures will lose their rigid character and become more and more flexible. For this reason it is necessary not only to calculate the rigid-body movements, but also simulate the deformations and use the results in the simulation of the movement of the robot. One, probably the most common, method of calculating this deformations I will show in the next subsection.
	\input{FEA.tex}
	\pagebreak
	\input{bibliography.tex}

\end{document}