\documentclass[11pt,english,a4paper,]{scrartcl}
\input{my_definitions.tex}

\title{Final Report about my Internship at VIT}
\author{Tobias Keute}

\begin{document}
\maketitle
\tableofcontents
\section{Cultural expieriences in India}
\section{Academic experiences at VIT}
\subsection{Ariving at \eigenname{Vellore Institute of Technology}}
When I arrived at the \vit\, I was brought to the Guest House, where I had to sit down, while someone took several phone calls to ask where my hostel is. After waiting for more than one hour the driver, who also took me from the airport drove me to three different hostels before they finally found the right hostel. There I also had to wait for half an hour, because they needed to tidy up my room first. My room was an air-conditioned six-bed room, but I was the only one staying there. The room was (for Indian standards) clean and ok.

\bigskip
Unfortunately I had no contact person, who showed me the campus or could help me at my first day, so I took a walk around the campus, totally unorientated, and tried to find Daniel Pascheka, who arrived one week before me. As I remembered the name of his block, I went there (which also took me a while, because I did not know nothing about the campus) and asked for the roomnumber of Daniel, but no one could help me and just a very few could speak proper english.

\bigskip
When I arrived back at my room, my neighbors came to welcome me and helped my getting connection to the internet (for details see "The Internet and Me"), so I could contact Daniel. My Neighbors helped me, although I only lived there for one week, more than all the VIT-offices together. 

\bigskip

\subsection{The laboratory and the "Hardware"}
\subsection{BureauCRAZY}
\end{document}